Analyzing the impact of social attributes on commit integration success

### 2017-02-21 Paper/MSRChallenge2017.tex
adjusted a sentence

Overall, this shows that while experience is not a perfect indicator, more
experienced developers are more likely to make high quality project commits.

>>>>

Overall, we have found that while experience is not a perfect indicator, 
experienced developers are more likely to make high quality project commits.
